Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
sdt

\section{Introduction}
Software inspections have since its inception [1] more than
25 years ago spawned quite some interest both from the
research community and industrial practice. The research
includes changes to the inspection process, e.g. [2], support to
the proceThe dependent variables are analyzed to evaluate the
hypotheses of the experiment. The main null and alternative
hypotheses [12] are stated below. These are evaluated for all
faults, class A faults and class A\&B faults. The hypotheses
concern efficiency, effectiveness and fault detecting
differences:ss, e.g. [3] and empirical studies, e.g. [4]. The
suggested improvements include active design reviews [5] and
perspective-based reading [6]. Industry has studied the
benefits of conducting software inspections [7].

@@

\subsection{Hypothesis}
The general hypothesis of the experiment is that Use-Case
Based Reading is more efficient and effective in finding faults
of the most critical fault classes, i.e. Checklist-Based Reading
is assumed to find more faults per time unit, and to find a
larger rate of the critical faults.
The dependent variables are analyzed to evaluate the
hypotheses of the experiment. The main null and alternative
hypotheses [12] are stated below. These are evaluated for all
faults, class A faults and class A\&B faults. The hypotheses
concern efficiency, effectiveness and fault detecting
differences:
\begin{itemize}
\item H\textsubscript{0 Eff} - There is no difference in efficiency (i.e.found faults per hour) between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritized use cases and the reviewers using a checklist.
\item H\textsubscript{0 Rate} - There is no difference in effectiveness (i.e. rate of faults found) between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{1 Rate} - There is a difference in effectiveness between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{0 Fault} - The reviewers applying use cases do not detect different faults than the reviewers using a checklist.
\item H\textsubscript{1 Fault} - The reviewers applying use cases detect different faults than the reviewers using a checklist.

@@

\Section{Results}

\subsection{There is no difference in efficiency}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.

\subsection{There is no difference in effectiveness}
The same test was chosen for Hrate, based on the same reasoning. The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.

@@

http://www.sussex.ac.uk/Users/grahamh/RM1web/WilcoxonTable2005.pdf

MWW = good for cont tests as well.
 Mann, Henry B.; Whitney, Donald R. (1947). ``On a Test of Whether one of Two Random Variables is Stochastically Larger than the Other''. Annals of Mathematical Statistics 18 (1): 50–60. doi:10.1214/aoms/1177730491. MR 22058. Zbl 0041.26103.

\Section{Tests for eff}

\Section{Tests for 3}

Chi-square test requirements[edit]
Quantitative data.
One or more categories.
Independent observations.
Adequate sample size (at least 10).
Simple random sample.
Data in frequency form.
All observations must be used.
\bibliographystyle{latex8}
\bibliography{latex8}

>>>>

\section{Introduction}
Software inspections have since its inception \cite{fagan2002design} more than
25 years ago spawned quite some interest both from the
research community and industrial practice. The research
includes changes to the inspection process, e.g. \cite{bisant1989two}, support to
the proceThe dependent variables are analyzed to evaluate the
hypotheses of the experiment. The main null and alternative
hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
faults, class A faults and class A\&B faults. The hypotheses
concern efficiency, effectiveness and fault detecting
differences:ss, e.g. \cite{basili1996empirical} and empirical studies, e.g. \cite{basili1999building}. The
suggested improvements include active design reviews \cite{parnas1985active} and
perspective-based reading \cite{shull2000perspective}. Industry has studied the
benefits of conducting software inspections \cite{weller1993lessons}.

@@

\subsection{Hypothesis}
The general hypothesis of the experiment is that Use-Case
Based Reading is more efficient and effective in finding faults
of the most critical fault classes, i.e. Checklist-Based Reading
is assumed to find more faults per time unit, and to find a
larger rate of the critical faults.
The dependent variables are analyzed to evaluate the
hypotheses of the experiment. The main null and alternative
hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
faults, class A faults and class A\&B faults. The hypotheses
concern efficiency, effectiveness and fault detecting
differences:

\begin{itemize}
\item H\textsubscript{0 Eff} - There is no difference in efficiency (i.e.found faults per hour) between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritized use cases and the reviewers using a checklist.
\item H\textsubscript{0 Rate} - There is no difference in effectiveness (i.e. rate of faults found) between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{1 Rate} - There is a difference in effectiveness between the reviewers applying use cases and the reviewers using a checklist.
\item H\textsubscript{0 Fault} - The reviewers applying use cases do not detect different faults than the reviewers using a checklist.
\item H\textsubscript{1 Fault} - The reviewers applying use cases detect different faults than the reviewers using a checklist.

@@

\Section{Results}
This section will cover the results of the experiment.

\subsection{Efficiency and Effectiveness A}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.

\subsection{Efficiency and Effectiveness B}
The same test was chosen for Hrate, based on the same reasoning. The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.

@@

\bibliographystyle{latex8}
\bibliography{latex8}
